---
title: "titanic1.Rmd"
output: html_document
---
```{r libraries}
# Required Libraries:
library(plyr)
library(lattice)
library(ggplot2)
setwd("~/Documents/R_place/kaggel_titanic")
```

# Titanic Dataset 1
  This is a first exploration of the Kaggel titanic data set.
 
 The variables included in this dataset are:
 
  * survival        Survival (0 = No; 1 = Yes)

  * pclass          Passenger Class (1 = 1st; 2 = 2nd; 3 = 3rd)
 
  * name            Name
 
  * sex             Sex

  * age             Age

  * sibsp           Number of Siblings/Spouses Aboard

  * parch           Number of Parents/Children Aboard

  * ticket          Ticket Number
  
  * fare            Passenger Fare

  * cabin           Cabin

  * embarked        Port of Embarkation (C = Cherbourg; Q = Queenstown; S = Southampton)
 
  The dataset is stored in a comma-separated-value (CSV) file and there are a total of 891 observations in this dataset.
  
```{r readingData, echo = TRUE}
test<- read.csv("./data/train.csv", header=TRUE, sep=",")
summary(test)
dim(test)
names(test)
length(unique(test$PassengerId))
```

